---
title: "Citation_Analytics"
author: "Maya Samet"
date: "7/16/2020"
output: html_document
---

```{r setup, include=FALSE}
setwd("/Users/samet/Documents/R/citation_analytics")
library(tidyverse)
library(rcrossref)
library(jsonlite)
library(ggplot2)
```

```{r}
abs_cit <- read.csv("adc_citation_keyword_search_ycomp.csv")
found_cit <- read.csv("Found_Citations.csv")
scythe_cit <- read.csv("scythe_search_results.csv")
```

```{r}
View(abs_cit)
View(found_cit)
View(scythe_cit)
```

Generate journal names (which journals do our citing articles belong to?)
```{r}
# regex for trimming dois
regex <- "10\\..*"

# function for retrieving journal names using article dois
journal_from_doi <- function(doi) {
  try(cr_cn(doi, format="citeproc-json-ish")[["container-title"]])
}

abs_cit_canonical <- abs_cit %>%
  # select only datasets with a single representational article
  filter(num_cit==1) %>%
  # trim article dois to correct format & creating empty journal field to populate
  mutate(article_doi=str_extract(article_doi, regex), journal="") 
  
# retrieving journal names using article dois
for (i in 1:nrow(abs_cit_canonical)){
  if (length(journal_from_doi(abs_cit_canonical$article_doi[i]) > 0)) {
    abs_cit_canonical$journal[i] <- journal_from_doi(abs_cit_canonical$article_doi[i])
  }
}

```

Replicate for all citations, not just canonical (canonical meaning singular data papers)
```{r}
abs_cit_all_journals <- abs_cit %>%
  # select only datasets with a single representational article
  filter(num_cit>1) %>%
  # trim article dois to correct format & creating empty journal field to populate
  mutate(article_doi=str_extract(article_doi, regex), journal="")

for (i in 1:nrow(abs_cit_all_journals)){
  if (length(journal_from_doi(abs_cit_all_journals$article_doi[i]) > 0)) {
    abs_cit_all_journals$journal[i] <- journal_from_doi(abs_cit_all_journals$article_doi[i])
  }
}

# Trimming & summing
temp_abs_cit_all <- abs_cit_all_journals %>% select(!(abstract:tips)) %>%
  mutate(journal = gsub(".*Geophysical Research.*","Journal of Geophysical Research", journal)) %>%
  mutate(journal = gsub("Climate Change Responses","Climate Change", journal)) %>%
  mutate(journal = gsub("Climatic Change","Climate Change", journal))

journal_sums_all <- table(temp_abs_cit_all$journal)[-1]
journal_freq_all <- prop.table(journal_sums_all)*100

View(journal_freq_all)
```

Journal Horiz Barchart (canonical)
```{r}
journal_sums_ord <- as.data.frame(journal_sums) %>%
  arrange(desc(Freq)) %>%
  mutate(Freq=as.numeric(Freq), Var1=as.character(Var1)) %>%
  rename(Journal = Var1, Count = Freq) 
  

p <- ggplot(journal_sums_ord, aes(x =reorder(Journal,Count), y = Count))+
  geom_col(width = 0.7) +
  coord_flip() + 
  scale_y_continuous(breaks=seq(0,10, by=2)) +
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank())
  
p

```

All Journal Horiz Barchart
```{r}
journal_sums_all_ord <- as.data.frame(journal_sums_all) %>%
  arrange(desc(Freq)) %>%
  mutate(Freq=as.numeric(Freq), Var1=as.character(Var1)) %>%
  rename(Journal = Var1, Count = Freq) 
  

p <- ggplot(journal_sums_all_ord, aes(x =reorder(Journal,Count), y = Count))+
  geom_col(width = 0.7) +
  coord_flip() + 
  scale_y_continuous(breaks=seq(0,20, by=1)) +
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank())
  
p

```

Writing citation pairs
```{r}
writ_cit_pairs <- function(cit_csv, json_name) {
  cit_pairs <- cit_csv %>%
    # trim dataset & article dois to correct format
    mutate(article_doi=str_extract(article_doi, regex),
           dataset_id=str_extract(dataset_id, regex)) %>%
    # subset rows
    filter(is_cited=="y") %>%
    # select relevant columns
    select(c(article_doi, dataset_id)) %>%
    # rename to work with citation pairs function
    rename(article_id = article_doi) %>%
    # make sure both have a value
    drop_na()
  
  # set working directory
  setwd("/Users/samet/Documents/R/citation_pairs")
  
  # function from scythe - write_citation_pairs.r - changed to be able to handle invalid dois
  
  bib <- cr_cn(cit_pairs$article_id, "bibtex")
  
  t <- tempfile()
  writeLines(unlist(bib), t)
  
  # import as a dataframe
  df <- bib2df::bib2df(t)
      
  # merge by DOI = article_id
  cit_pairs_merge <- cit_pairs %>%
    rename(DOI = article_id)
  
  df <- left_join(df, cit_pairs_merge, by="DOI")
  
      # rename for database ingest
      cit_full <- df %>%
          dplyr::rename(target_id = .data$dataset_id,
                 source_id = .data$DOI,
                 source_url = .data$URL,
                 origin = .data$AUTHOR,
                 title = .data$TITLE,
                 publisher = .data$PUBLISHER,
                 journal = .data$JOURNAL,
                 volume = .data$VOLUME,
                 page = .data$PAGES,
                 year_of_publishing = .data$YEAR) %>%
          dplyr::select(.data$target_id, .data$source_id, .data$source_url, .data$origin, .data$title,
                        .data$publisher, .data$journal, .data$volume, .data$page, .data$year_of_publishing)%>%
          dplyr::mutate(id = NA, report = NA, metadata = NA, link_publication_date = Sys.Date()) #%>%
          #dplyr::mutate(publisher = ifelse(.data$publisher == "Elsevier {BV", "Elsevier", "Copernicus"))
  
  write_json(cit_full, json_name)
}
  
```

Generate number of flagged datasets
```{r}
abs_cit_pairs %>%
  select(dataset_id) %>%
  distinct() %>%
  nrow()

#it's 65
```

Generate number of secondary citations
```{r}
# regex for trimming dois
regex <- "10\\..*"

# function for retrieving cit num using article dois
cit_num_from_doi <- function(doi) {
  try(cr_citation_count(doi)$count)
}

abs_cit_gooddoi <- abs_cit %>%
  mutate(article_doi=str_extract(article_doi, regex), journal="") %>%
  # select only datasets with citations
  filter(num_cit>0, !is.na(article_doi)) 
  # trim article dois to correct format & creating empty journal field to populate
   
  
# retrieving journal names using article dois
for (i in 1:nrow(abs_cit_gooddoi)){
  if (length(cit_num_from_doi(article_doi)> 0)) {
    abs_cit_gooddoi$journal_cit_count[i] <- cit_num_from_doi(abs_cit_gooddoi$article_doi[i])
  }
}

View(abs_cit_gooddoi)

```

Secondary Citations Histogram
```{r}
ggplot(abs_cit_gooddoi, aes(x=journal_cit_count)) + 
  geom_histogram(binwidth=25, color="white", boundary=0) + 
  xlab("number of citations")+
  ylab("count") + 
  scale_x_continuous(breaks=seq(0, 450, by=25)) +
  scale_y_continuous(breaks=seq(0, 100, by=5))
```

Citations Per Dataset
```{r}
cit_per_ds <- abs_cit_gooddoi %>%
  select(dataset_url, num_cit) %>%
  distinct()

ggplot(cit_per_ds, aes(x=num_cit)) + 
  geom_histogram(binwidth=1, color="white") + 
  xlab("number of citations")+
  ylab("count") + 
  scale_x_continuous(breaks=seq(1, 450, by=1)) +
  scale_y_continuous(breaks=seq(0, 100, by=5))
```