---
title: "Dataset Abstract Search"
author: "Maya Samet"
date: "9/22/2020"
output: html_document
---

```{r setup, include=FALSE, cache=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(stringr)
library(dplyr)
library(readr)

# load in categorization data
abstracts_df<-read_csv("dataset_categorization.csv") %>% 
  select(url, id, abstract)
```

## ADC Citation Search

Using R stringr package & regex techniques to search through the abstracts of datasets in the Arctic Data Center for references to dataset citations in articles.

### Using regexes for text search with `stringr::str_extract`

Here's an example of how to use `stringr::str_extract` for regex searches. I'm going to select a long abstract I found from preloaded abstracts dataset. Somewhere in this abstract there is a reference to a connected publication. 

```{r}
sample_abstract <- abstracts_df[64,3]
sample_abstract
```

Too long, did not read. Instead of reading through the entire abstract for publication mentions we can use this regex, which when used as the `pattern` argument of `stringr::str_extract_all` will capture and return the entire sentence(s) that the chosen keyword "publish/publication" is found in.

```{r}
publication_regex <- "[^.!?]*publi(?:sh|cation)[^.!?]*"
str_extract(sample_abstract, publication_regex)

# You can run `str_extract` on a list too
str_extract_all(c("irrelevant abstract", sample_abstract, "This is an oceanography dataset. It was used in a publication.", "We collected this data. The data was published"), publication_regex)
```


Reading through extracted text from the abstracts is much easier than reading through the abstracts themselves. Let's jazz the regex up a bit to look for terms like "article" and "paper" as well and search through all ADC abstracts. This might take a few minutes to run

```{r, cache=FALSE}
regex <- "[^.!?]*(?:article|paper|journal|publi(?:sh|cation))[^.!?]*"

# This code creates a df including only dois & abstracts that triggered the regex
# and adds a column with the extracted text. 
abstracts_extracted <- abstracts_df %>%
  mutate(citation_reference=paste(str_extract_all(abstract, regex))) %>%
  filter(citation_reference != "character(0)")

head(abstracts_extracted$citation_reference)
```

Now saving the csv
```{r}
#write.csv(abstracts_extracted, file="adc_publication_keyword_search_pt1_raw.csv")

```

---

Returning to this document 3 months later with a few more abstract search terms I'd like to try - et al./et alia, (name year) e.g. (Jones 2014), and direct mentions of the word citation/cited. 
```{r}
regex2 <- "[^.!?]*\\b(?:et al|\\(.*\\d{4}\\)|cit(?:ation|ed))[^.!?]*"

# This code creates a df including only dois & abstracts that triggered the regex
# and adds a column with the extracted text. 
abstracts_extracted2 <- abstracts_df %>%
  mutate(citation_reference=paste(str_extract_all(abstract, regex2))) %>%
  filter(citation_reference != "character(0)")
```
```{r}
head(abstracts_extracted)
```
Now to filter out results appearing in the last abstract search:

```{r}
abstracts_extracted2<-anti_join(abstracts_extracted2, abstracts_extracted, by="id")

```

```{r}
#write.csv(abstracts_extracted2, file="adc_publication_keyword_search_pt2_raw.csv")

```
